---
title: "lab_7"
author: "Tian Walker, Dominik Grätz, Amber Somarriba, Brittany Spinner, Rachel Miller-Moudgil"
date: "2022-11-03"
output: pdf_document
bibliography: ref.bib
---

# commit 1 (code hidden)
```{r Commit 1 setup, include=FALSE, warning=TRUE}
knitr::opts_chunk$set(echo = TRUE, fig.height=8, fig.width=6.5)
library(rio)
library(here)
library(tidyverse)

star <- import(here("data", "star.csv"))

```

# commit 3
```{r Commit 3, echo=FALSE, message=FALSE}

#head(star)

star_df <- star %>% 
  group_by(sex, frl) %>% 
  summarize(math_mean = mean(tmathss),
math_sd = sd(tmathss),
rdg_mean = mean(treadss),
rdg_sd = sd(treadss)) 

knitr::kable(star_df, booktabs = TRUE)
```
The scores `r star_df$math_mean` represent ( _in order_ ) the mean math scores for boys _without_, boys _with_, and girls _without_, and girls _with_ free or reduced price lunches in this data sample. The standard deviation of the math mean scores `r star_df$math_sd` represent ( _in order_ ) the standard deviation of math scores for boys _without_, boys _with_, and girls _without_, and girls _with_ free or reduced price lunches in this data sample. The  scores `r star_df$rdg_mean` represent the mean reading scores for boys _without_, boys _with_, and girls _without_, and girls _with_ free or reduced price lunches in this sample. And the standard deviation of reading scores `r star_df$rdg_sd` represent the standard deviation of reading scores for for boys _without_, boys _with_, and girls _without_, and girls _with_ free or reduced price lunches in this data sample.



# commit 4
```{r Commit 4, echo=FALSE, warning=TRUE, message=FALSE}
star$frl <- factor(star$frl)


ggplot(star, aes(x = totexp, y = tmathss)) +
  geom_point(color = "grey") + 
  geom_smooth(aes(color = frl), method = "lm")+
  labs(title = "Relation between teacher experience and math scores",
         subtitle = "Separate regression lines displayed by freereduces price lunch status",
         x = "Teacher Experience (years)",
         y = "Total Math Scale Score", 
       color = "Lunch status")+
  scale_color_discrete(breaks = c("yes", "no"), labels = c("yes" = "Free/Reduced Price Meals", "no" = "Paid Meals"))+
  #scale_color_discrete(breaks = c("yes", "no"))+
  theme_minimal() +
  theme(legend.position = "bottom")

#dominiks version
#test
```


\newpage
# References 

@BUDDIN2009103


@CLOTFELTER2007673


@KUKLAACEVEDO200949


@KANE2008615



